### 2023-03-04 manuscript.tex
Adding CSS for section numbering. [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/540c54a0e1a9c1b107387aa297db8144b6a79d5e.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/540c54a0e1a9c1b107387aa297db8144b6a79d5e/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4332996437

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/003c9db3c507b7e3b0f010f1c8f579bac7ba666d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/003c9db3c507b7e3b0f010f1c8f579bac7ba666d}{SORTEE-Github-Hackathon/manuscript@003c9db}
on March 4, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/540c54a0e1a9c1b107387aa297db8144b6a79d5e/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/540c54a0e1a9c1b107387aa297db8144b6a79d5e}{SORTEE-Github-Hackathon/manuscript@540c54a}
on March 4, 2023.
